Fair Queuing Aware Congestion Control

### 2022-09-25 tex/paper.tex
Add figures

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{{"../sample/plots/concept_fq"}.pdf}
\caption{In case there is \textbf{fair queuing}, when the bottleneck link is congested, subflow 1, which sends more, sees increasing queuing delay. Subflow 2 doesn't see increased queuing delay as it sends less than its fair share and thus its packets don't have to wait at the bottleneck link.}
\label{fig:illustration_fq}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{{"../sample/plots/concept_fcfs"}.pdf}
\caption{In case there is \textbf{no fair queuing}, when the bottleneck link is congested, a queue builds up. Since both subflows share the same queue, they both see increased queuing delay.}
\label{fig:illustration_no_fq}
\end{figure}

>>>>

\begin{figure}[h]
\centering 
\subfloat[\footnotesize A host sending data to a receiver. There is a bottleneck link with a switch which applies \textbf{fair queuing}.]{\includegraphics[width=\columnwidth]{{"figures/fq"}.pdf}
\label{fig:fq_overview}}\\
\subfloat[\footnotesize Queuing delay in case of \textbf{fair queuing}.]{
\includegraphics[width=\columnwidth]{{"../sample/plots/concept_fq"}.pdf}
\label{fig:fq_detail}}
\caption{In case there is \textbf{fair queuing}, when the bottleneck link is congested, subflow 1, which sends more, sees increasing queuing delay. Subflow 2 doesn't see increased queuing delay as it sends less than its fair share and thus its packets don't have to wait at the bottleneck link.}
\label{fig:illustration_fq}
\end{figure}

\begin{figure}[h]
\centering
\subfloat[\footnotesize A host sending data to a receiver. There is a bottleneck link with a switch which applies \textbf{no fair queuing}.]{\includegraphics[width=\columnwidth]{{"figures/no_fq"}.pdf}
\label{fig:no_fq_overview}}\\
\subfloat[\footnotesize Queuing delay in case there is \textbf{no fair queuing}.]{
\includegraphics[width=\columnwidth]{{"../sample/plots/concept_fcfs"}.pdf}
\label{fig:no_fq_detail}}
\caption{In case there is \textbf{no fair queuing}, when the bottleneck link is congested, a queue builds up. Since both subflows share the same queue, they both see increased queuing delay.}
\label{fig:illustration_no_fq}
\end{figure}
